A Linear Regression Model for Predicting MSDN Forums Votes

### 2018-10-31 forums/postScraping/msdn.forums - Copy.rmd
MLR

library(dplyr)
library(mosaic)
library(stringr) # Ref: https://sebastiansauer.github.io/dplyr_filter/
library(plotly)

@@

>>>>

library(dplyr)
#library(mosaic)
library(stringr) # Ref: https://sebastiansauer.github.io/dplyr_filter/
library(plotly)

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
vcrcv = subset(forums, select=(c('viewCount','replyCount','votes', 'threadState')))
vc <- forums$viewCount[0:200]
rc <- forums$replyCount[0:200]
v  <- forums$votes[0:200]
#lm( v ~ log(vc), data=vcrcv)
fit2 = lm( v ~ vc + rc, data = vcrcv, na.action=na.pass)
summary(fit2)
cat('Confidence Interval ',confint(fit2))
summary(fit2)$coefficients

isError <- is.na(v) || is.nan(v) || is.infinity(v)

```{r}

### 2018-10-31 forums/postScraping/msdn.forums.rmd
MLR

The correlation between replyCount and votes was greater than 0.5 and not considered here. So the focus was then more towards viewCount and votes. Among the three, the number of views and the number of replies were least coreleated, while between the number of votes and the number replies the correlation pronounced most.

@@

## Considering Linear Regression Between votes and viewCount

@@

### For votes and viewCount, examining 
$$\hat{votes} = \beta~0 + \beta~1 * viewCount$$

@@

FITvvc <- lm( v ~ log(vc), data=vcrcv)

summary(FITvvc)
cat('Confidence Interval ',confint(FITvvc))
summary(FITvvc)$coefficients

print(c('beta0',summary(FITvvc)$coefficients[1,1]))
print(c('beta1',summary(FITvvc)$coefficients[2,1]))

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
#Normality
qqnorm(log(FITvvc$residuals))
qqline(log(FITvvc$residuals))
plot(FITvvc)
#influencePlot(FITvvc)
```

@@

## And

Apply $\beta~0$ and $\beta~1$ into the model,
$$\hat{votes} = -5.363812 + 1.195719 * viewCount$$
Notice throughout the analysis, all numbers are logarithmic. Therefore

- when $$\hat{votes}= 1$$, 
$$viewCount = exp(1+5.363812/1.195719)$$

```{r echo=FALSE, message=FALSE, warning=FALSE}
view_count = exp(
  (1+abs(summary(FITvvc)$coefficients[1,1]))/(summary(FITvvc)$coefficients[2,1])
)
view_count

*This simple linear model therefore predicts an estimated and average 204 views for receiving a vote.*

@@

fit1 = lm( vcrcv$votes ~ vcrcv$viewCount , data = vcrcv)

pfit1  = RegressionPlots(fit1)

@@

## Experimenting and still under investigation

Multiple linear regression model:

$$\hat{votes} = \beta~0 + \beta~1 * viewCount + \beta~2 * replyCount$$

```{r echo=FALSE, message=FALSE, warning=FALSE, eval=TRUE}

fit2 = lm( vcrcv$votes ~ vcrcv$viewCount + vcrcv$replyCount, data = vcrcv)

pfit2  = RegressionPlots(fit2)

pfit2

>>>>

The correlation between among the three is expected.

@@

## Considering Multiple Linear Regression

The intent here is to investigate how a multiple linear regression model may fit.

@@

### Considering
$$\hat{votes} = \beta~0 + \beta~1 * viewCount + \beta~2 * replyCount$$

@@

vcrcv = subset(forums, select=(c('viewCount','replyCount','votes', 'threadState')))

vc200 <- forums$viewCount[0:200]
rc200 <- forums$replyCount[0:200]
v200  <- forums$votes[0:200]

vc1000 <- forums$viewCount[0:1000]
rc1000 <- forums$replyCount[0:1000]
v1000  <- forums$votes[0:1000]

vc2000 <- forums$viewCount[0:2000]
rc2000 <- forums$replyCount[0:2000]
v2000  <- forums$votes[0:2000]

vc <- forums$viewCount
rc <- forums$replyCount
v  <- forums$votes

@@

### Start with the first 200 observations

```{r}
fit200 = lm( v200 ~ vc200 + rc200, data = vcrcv)
summary(fit200)
cat('Confidence Interval ',confint(fit200))
summary(fit200)$coefficients

#print(c('beta0',summary(fit200)$coefficients[1,1]))
#print(c('beta1',summary(fit200)$coefficients[2,1]))

```{r}
qqnorm(fit200$residuals)
qqline(fit200$residuals)
plot(fit200)
#influencePlot(fit1000)
```

### Take the first 1000 observations

```{r}
fit1000 = lm( v1000 ~ vc1000 + rc1000, data = vcrcv)
summary(fit1000)
cat('Confidence Interval ',confint(fit1000))
summary(fit1000)$coefficients

#print(c('beta0',summary(fit200)$coefficients[1,1]))
#print(c('beta1',summary(fit200)$coefficients[2,1]))

```{r}
qqnorm(fit1000$residuals)
qqline(fit1000$residuals)
plot(fit1000)
#influencePlot(fit1000)
```

### Consider the first 2000 observations

```{r}
fit2000 = lm( v2000 ~ vc2000 + rc2000, data = vcrcv)
summary(fit2000)
cat('Confidence Interval ',confint(fit2000))
summary(fit2000)$coefficients

#print(c('beta0',summary(fit2000)$coefficients[1,1]))
#print(c('beta1',summary(fit2000)$coefficients[2,1]))

```{r}
qqnorm(fit2000$residuals)
qqline(fit2000$residuals)
plot(fit2000)
```

### Take all observations

```{r}
fitall = lm( v ~ vc + rc, data = vcrcv)
summary(fitall)
cat('Confidence Interval ',confint(fitall))
summary(fitall)$coefficients

#print(c('beta0',summary(fitall)$coefficients[1,1]))
#print(c('beta1',summary(fitall)$coefficients[2,1]))

```{r}
qqnorm(log(fitall$residuals))
qqline(log(fitall$residuals))
plot(fitall)
```

@@

@@

fit1000 = lm( v1000 ~ vc1000 + rc1000 , data = vcrcv)

pfit1  = RegressionPlots(fit1000)

@@
